Clean data

### 2020-11-29 analysis/02_clean-data.Rmd
Modified the labeling in 02_clean-data (again) so that it all lives there and no additional clean-up is needed in 04_figs-tables

      levels = c("Rarely", "Once a week", "At least once a day")

@@

      factor(Q2.2, labels = c("Always", "Sometimes", "Never")), 

@@

@@

      levels = c("Not often", "Often")

@@

      levels = c("More than once a month, less than once a year", "At least once a month")

@@

      labels = c(

@@

        "$1000-$4,999", "$5000-$9,999", "$10,000+"),

@@

      labels = c(

@@

@@

      labels = c(

@@

      factor(Q2.9, labels = c("Yes", "No")), 
      c("No", "Yes")

@@

      levels = c("Haven't volunteered in past 12 months", "Rarely", "More than once a month, less than once a year", "At least once a month")

@@

      factor(Q5.1, labels = c("Yes", "No")), 
      c("No", "Yes")

@@

      labels = c(

@@

@@

      levels = c("Not involved", "Involved")

@@

      levels = c("Not involved", "Involved")

@@

      labels = c(

@@

      factor(Q5.7, labels = c("Yes", "No")), 
      c("No", "Yes")

@@

      levels = c("Not sure", "Rarely", "At least once a month")

@@

      levels = c("Not important", "Important")

@@

      labels = c(

@@

        "Muslim", "Sikh", "Hindu", "Buddhist", "Atheist", "Other"), 

@@

        labels = c(

@@

@@

        c(

@@

      labels = c(

@@

      labels = c(

@@

      labels = c(

@@

      levels = c("Less than median", "More than median")

@@

@@

      levels = c("Less than median", "More than median")

>>>>

      levels = c("Rarely", "Once a week", "At least once a day"),
      labels = str_c(
        "Follow national news: ",
        c("Rarely", "Once a week", "At least once a day")

@@

        Q2.2, 
        labels = str_c(
          "Follow international news: ", 
          c("Always", "Sometimes", "Never")
      str_c(
        "Follow international news: ", 

@@

    Q2.3_1 = factor(Q2.3_1, labels = str_c("Medium to follow news: ", c("No TV", "TV"))),
    Q2.3_2 = factor(Q2.3_2, labels = str_c("Medium to follow news: ", c("No Print", "Print"))),
    Q2.3_3 = factor(Q2.3_3, labels = str_c(
      "Medium to follow news: ", 
      c("No Online (excluding social media)", "Online (excluding social media)")
    )),
    Q2.3_4 = factor(Q2.3_4, labels = str_c(
      "Medium to follow news: ", 
      c("No Social media", "Social media")
    )),
    Q2.3_5 = factor(Q2.3_5, labels = str_c("Medium to follow news: ", c("No Radio", "Radio"))),
    Q2.3_6 = factor(Q2.3_6, labels = str_c(
      "Medium to follow news: ", 
      c("No Email newsletters", "Email newsletters")
    )),
    Q2.3_7 = factor(Q2.3_7, labels = str_c(
      "Medium to follow news: ", 
      c("No News app", "News app")
    )),

@@

      levels = c("Not often", "Often"),
      labels = str_c(
        "Follow government and public affairs: ",
        c("Not often", "Often")

@@

      levels = c("More than once a month, less than once a year", "At least once a month"),
      labels = str_c(
        "Donation frequency: ",
        c("More than once a month, less than once a year", "At least once a month")

@@

      labels = str_c("Donated last year: ", c(

@@

        "$1000-$4,999", "$5000-$9,999", "$10,000+")),

@@

      labels = str_c("Importance of trusing charities: ", c(

@@

      )),

@@

      labels = str_c("Trust in charities: ", c(

@@

      factor(Q2.9, labels = str_c("Volunteered in past 12 months: ", c("Yes", "No"))), 
      str_c("Volunteered in past 12 months: ", c("No", "Yes"))

@@

      levels = c("Haven't volunteered in past 12 months", "Rarely", "More than once a month, less than once a year", "At least once a month"),
      labels = str_c(
        "Volunteer frequency: ",
        c("Haven't volunteered in past 12 months", "Rarely", "More than once a month, less than once a year", "At least once a month")

@@

      factor(Q5.1, labels = str_c("Voted in last election: ", c("Yes", "No"))), 
      str_c("Voted in last election: ", c("No", "Yes"))

@@

      labels = str_c("Liberal to Conservative: ", c(

@@

    # *Q5.3*: Here is a list of different types of voluntary organizations. For each organization, indicate whether you are an active member, an inactive member, or not a member of that type of organization:
    # |                                         | Active member | Inactive member | Don't belong |
    # | --------------------------------------- | :-----------: | :-------------: | :----------: |
    # | Church or religious organization        |       •       |        •        |      •       |
    # | Sport or recreational organization      |       •       |        •        |      •       |
    # | Art, music, or educational organization |       •       |        •        |      •       |
    # | Labor union                             |       •       |        •        |      •       |
    # | Political party                         |       •       |        •        |      •       |
    # | Environmental organization              |       •       |        •        |      •       |
    # | Professional association                |       •       |        •        |      •       |
    # | Humanitarian or charitable organization |       •       |        •        |      •       |
    # | Consumer organization                   |       •       |        •        |      •       |
    # | Other organization                      |       •       |        •        |      •       |
    Q5.3_1 = fct_relevel(
      factor(Q5.3_1, labels = str_c(
        "Church or religious organization: ", 
        c("Active member", "Inactive member", "Don't belong"))
      str_c(
        "Church or religious organization: ", 
        c("Don't belong", "Inactive member", "Active member")
    Q5.3_2 = fct_relevel(
      factor(Q5.3_2, labels = str_c(
        "Sport or recreational organization: ",
        c("Active member", "Inactive member", "Don't belong"))
      str_c(
        "Sport or recreational organization: ",
        c("Don't belong", "Inactive member", "Active member")
    Q5.3_3 = fct_relevel(
      factor(Q5.3_3, labels = str_c(
        "Art, music, or educational organization: ",
        c("Active member", "Inactive member", "Don't belong"))
      str_c(
        "Art, music, or educational organization: ",
        c("Don't belong", "Inactive member", "Active member")
    Q5.3_4 = fct_relevel(
      factor(Q5.3_4, labels = str_c(
        "Labor union: ",
        c("Active member", "Inactive member", "Don't belong"))
      str_c(
        "Labor union: ",
        c("Don't belong", "Inactive member", "Active member")
    Q5.3_5 = fct_relevel(
      factor(Q5.3_5, labels = str_c(
        "Political party: ",
        c("Active member", "Inactive member", "Don't belong"))
      str_c(
        "Political party: ",
        c("Don't belong", "Inactive member", "Active member")
    Q5.3_6 = fct_relevel(
      factor(Q5.3_6, labels = str_c(
        "Environmental organization: ",
        c("Active member", "Inactive member", "Don't belong"))
      str_c(
        "Environmental organization: ",
        c("Don't belong", "Inactive member", "Active member")
    Q5.3_7 = fct_relevel(
      factor(Q5.3_7, labels = str_c(
        "Professional association: ",
        c("Active member", "Inactive member", "Don't belong"))
      str_c(
        "Professional association: ",
        c("Don't belong", "Inactive member", "Active member")
    Q5.3_8 = fct_relevel(
      factor(Q5.3_8, labels = str_c(
        "Humanitarian or charitable organization: ",
        c("Active member", "Inactive member", "Don't belong"))
      str_c(
        "Humanitarian or charitable organization: ",
        c("Don't belong", "Inactive member", "Active member")
    Q5.3_9 = fct_relevel(
      factor(Q5.3_9, labels = str_c(
        "Consumer organization: ",
        c("Active member", "Inactive member", "Don't belong"))
      str_c(
        "Consumer organization: ",
        c("Don't belong", "Inactive member", "Active member")
    Q5.3_10 = fct_relevel(
      factor(Q5.3_10, labels = str_c(
        "Other organization: ",
        c("Active member", "Inactive member", "Don't belong"))
      str_c(
        "Other organization: ",
        c("Don't belong", "Inactive member", "Active member")

@@

      levels = c("Not involved", "Involved"),
      labels = str_c(
        "History of activism: ",
        c("Not involved", "Involved")

@@

      levels = c("Not involved", "Involved"),
      labels = str_c(
        "History of family activism: ",
        c("Not involved", "Involved")

@@

      labels = str_c("Trust in political institutions: ",c(

@@

      factor(Q5.7, labels = str_c("Traveled to a developing country: ", c("Yes", "No"))), 
      str_c("Traveled to a developing country: ", c("No", "Yes"))

@@

      levels = c("Not sure", "Rarely", "At least once a month"),
      labels = str_c(
        "Religious and worship service attendance: ",
        c("Not sure", "Rarely", "At least once a month")

@@

      levels = c("Not important", "Important"),
      labels = str_c(
        "Importance of religion: ",
        c("Not important", "Important")

@@

      labels = str_c("Religion: ", c(

@@

        "Muslim", "Sikh", "Hindu", "Buddhist", "Atheist", "Other")), 

@@

        labels = str_c("People should be more charitable: ", c(

@@

        ))

@@

      str_c("People should be more charitable: ", c(

@@

      labels = str_c("Gender: ", c(

@@

      labels = str_c("Marital status: ", c(

@@

      labels = str_c("Education: ", c(

@@

      levels = c("Less than median", "More than median"),
      labels = str_c(
        "Income: ",
        c("Less than median", "More than median")

@@

    Q5.16_1 = factor(Q5.16_1, labels = str_c("Race: ", c("Not White", "White"))),
    Q5.16_2 = factor(Q5.16_2, labels = str_c(
      "Race: ", c("Not Black or African American", "Black or African American"))
    Q5.16_3 = factor(Q5.16_3, labels = str_c(
      "Race: ", c("Not American Indian or Alaska Native", "American Indian or Alaska Native"))
    Q5.16_4 = factor(Q5.16_4, labels = str_c("Race: ", c("Not Asian", "Asian"))),
    Q5.16_5 = factor(Q5.16_5, labels = str_c(
      "Race: ", 
      c("Not Native Hawaiian or Pacific Islander", "Native Hawaiian or Pacific Islander")
    )),
    Q5.16_6 = factor(Q5.16_6, labels = str_c("Race: ", c("Not Other", "Other"))),

@@

      levels = c("Less than median", "More than median"),
      labels = str_c(
        "Age: ", 
        c("Less than median", "More than median")
